Comment: Inferring Trade Costs from Trade Booms and Trade Busts

### 2016-06-07 Paper/Manuscript.tex
Changement de bibliographie ?
Changement de l'affiliation de Claire
Essai

\documentclass{article}
\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[pdftex]{graphicx}  
%Langue utilisée
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\emergencystretch=8em
\usepackage[margin=1in]{geometry}

@@

\author[1]{Guillaume Corlay}
\author[2]{Stéphane Dupraz}
\author[1]{Claire Labonne}
\author[1]{Anne Muller}
\author[3]{Guillaume Daudin\footnote{Corresponding author: guillaume.daudin@dauphine.fr, }\footnote{We are grateful to Celine Antonin (OFCE) for her constant supply of helpful comments. She, of course, bears no responsibility for remaining errors.}}
\affil[1] {ENSAE, French National School of Statistics and Economic Administration, 3, avenue Pierre Larousse, 92245 Malakoff, FRANCE}
\affil[2] {Columbia University, 10025 New York NY, USA}
\affil[3] {Université Paris-Dauphine, PSL Research University, LEDa, 75016 PARIS, FRANCE
Université Paris-Dauphine, PSL Research University, LEDa, UMR [225], DIAL, 75016 PARIS, FRANCE

SciencesPo, Observatoire Français des Conjonctures Économiques (OFCE), 75007, PARIS, FRANCE}

@@

\bibliographystyle{apalike}
\bibliography{bibliography}

>>>>

\documentclass{article}
\usepackage{authblk}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[pdftex]{graphicx}  
%Langue utilisée
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\emergencystretch=8em
\usepackage[margin=1in]{geometry}

@@

\author[1]{Guillaume Corlay}
\author[2]{Stéphane Dupraz}
\author[4]{Claire Labonne}
\author[1]{Anne Muller}
\author[3]{Guillaume Daudin\footnote{Corresponding author: guillaume.daudin@dauphine.fr, }\footnote{We are grateful to Celine Antonin (OFCE) for her constant supply of helpful comments. She, of course, bears no responsibility for remaining errors.}}
\affil[1] {ENSAE, French National School of Statistics and Economic Administration, 3, avenue Pierre Larousse, 92245 Malakoff, FRANCE}
\affil[2] {Columbia University, 10025 New York NY, USA}
\affil[3] {Université Paris-Dauphine, PSL Research University, LEDa, 75016 PARIS, FRANCE
Université Paris-Dauphine, PSL Research University, LEDa, UMR [225], DIAL, 75016 PARIS, FRANCE

Sciences Po, Observatoire Français des Conjonctures Économiques (OFCE), 75007, PARIS, FRANCE}

\affil[4] { Paris School of Economics / Université Paris 1 Panthéon Sorbonne -- ACPR - Banque de France, 75009, PARIS, FRANCE}

@@

\bibliographystyle{aer}
\bibliography{bibliography}
